---
title: "Lab 7 - Multiple Linear Regressions"
author: "Erin de Leon Sanchez"
date: "11/8/2021"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs

Use GGally::ggpairs() function to create a pairs plot. 

```{r}
ggpairs(penguins)
```


```{r}
penguins %>%  
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

## Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass). 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Return just the coefficients:
penguin_lm

```

How would you interpret this coefficient for flipper length (51.54)?
On average, we would expect a 1 mm increase in flipper length to be associated with a 51.54 g increase in penguin body mass, if everything else is constant. 

Use `summary()` function to get more information

```{r}
summary(penguin_lm)
```

Meaning of the r^2 value: 76% of variance in the body mass is predictable from the bill depth and flipper length.

### Use `broom` function tidy and glance 

Use broom::tidy to get the coefficient summary in a data frame. 
Use broom::glance to get the model summary in a data frame. 

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to the bill depth coefficient. 

`r penguin_lm_tidy$estimate[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

## Try another model

We have thought really hard, done a lit review, consulted with experts, deeply explored out data, and decided that the three most critical variables to include in this model (with body mass as the outcome variable) are:

- flipper length
- species
- sex

Task: Create a multiple linear regression model using those 3 predictor variables

Then take a look at the model outputs then interpret the coefficients with a neighbor

```{r}
penguin_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_2
```

mass(g) = -365.82 + 20.02(flipperlength(mm)) - 87.63(chinstrap) + 836.26(Gentoo) +530.38(male)
KEEP IN MIND OUR REFERENCES ARE Adelie and Male
If everything else is the same, on average, we expect a Gentoo penguin to weigh 836.26 g more than an Adelie penguin. 
If everything else is held constant, on average, we expect a Chinstrap penguin to weigh 87.63 g less than an Adelie penguin.
If everything else is the same, then we expect a male penguin to weigh on average 530.38 g more than a female penguin.

### Use broom::augment() to see predicted values

```{r}
augment(penguin_lm_2)
```

## Use plot() to look at model diagnostics 

```{r}
plot(penguin_lm_2)
```

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are reasonable predictor variable (make sure you're thinking hard about variables and different variable combinations)
- Diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers (<< last one not an assumption)


## Make output tables

Using modelsummary
```{r}
modelsummary(penguin_lm_2) 
```

Using stargazer:

```{r, results = "asis"}
stargazer(penguin_lm_2, type = "html")
```

